---
title: 'RMarkdown:  In Class Assignment'
author: "Bryce Borak"
date: "Data 2401"
output: 
  html_document:
    toc: TRUE
    toc_depth: 3
---


```{r setup, include=FALSE}
# Everything in this chunk is R code. 
# You are not expected to understand or edit this yet. 
# We will talk about what this does in a later class, with a little preview in part 2.
knitr::opts_chunk$set(echo = TRUE) 
```


Reminders: 

- You do not need to memorize Markdown syntax.
- You are expected to look things up using:
   - RStudio’s Markdown Help
   - Online documentation or examples
- Click Knit as you go to check that your document still renders correctly.
- Commit at the end, but consider committing as you go as well. 



# Part 1: Markdown Practice


## Wise Words 
>"Some succeed because they are destined.Others succeed because they are determined."
[https://www.brainyquote.com/authors/jason-witten-quotes]

## I recommend
### James Hatfield
>"I'm your dream,make you real.I'm your eyes when you must steal.

-*Enter Sandman*
-*Sad but true* 
-*One*

# Part 2: Code Chunks

```{r echo = TRUE}
2 + 2
```

Complete the following steps:

  - What changed between the two outputs? The change between the outputs was that it did not show the full equation rather than just the answer.Yes the calculation still ran when the code was hidden.Maybe if it was a major equation and would rather just see the end result and why they would want to is to see the full process.
 
  
# Part 3: A small R-in-markdown preview

## About this document
- This document is about learning how o use block code and make a list for part 1. Part 2 dives into more knitting code and understanding what is does and how it works.`r Sys.Date()`is an inline R code.

# Submitting Instructions

When you are finished: 

- Knit the document so that it produces an html file.
- Stage, commit, and push:
  - The updated `.rmd` file 
  - The generated `.html` file
- Submit the GitHub link to the assignment on Canvas.
 
